|

### 2023-05-16 paper/05-discussion.Rmd
Small grammar edits.

# Discussion {#sec:discussion}

In this work, we have proposed STRAIN - a simple and interpretable statistic for evaluating pass rushers, with higher STRAIN values corresponding to greater pass rushing ability. We demonstrated that a pass rusher's average STRAIN is both stable and more predictive of future pressure events than using the player's previously observed pressure events. This is analogous to the use of exit velocity in baseball, a predictive measurement that avoids the noisy nature of observed outcomes, emphasizing how the opportunity of working with player-tracking data can lead to the development of insightful metrics in American football.

>>>>

# Discussion {#sec:discussion}
In this work, we have proposed STRAIN - a simple and interpretable statistic for evaluating pass rushers - with higher values corresponding to greater pass rushing ability. We demonstrated that a pass rusher's average STRAIN is both stable and more predictive of future pressure events than using the player's previously observed pressure events. This is analogous to the use of exit velocity in baseball, a predictive measurement that avoids the noisy nature of observed outcomes, emphasizing how the opportunity of working with player-tracking data can lead to the development of insightful metrics in American football.
